parasitemia

### 2023-06-12 Scripts/R/markdown_files/response_to_reviewers.Rmd

```

```{r data}

# read in data

df_hbox <- read_csv(paste0(base_dir, "Data/master_datatable.csv")) %>% 
  as_tibble() %>% 
  janitor::clean_names() %>% 
  mutate(status = replace(status, status == "HV", "HC")) %>%

  dplyr::filter(status %in% c("CM", "HC", "UM") & session_no == 1 | subject_id == "TM0003CM01") %>% 
  dplyr::filter(!grepl("blood", subject_id)) %>% 
  mutate(status = factor(status, levels = c("HC", "UM", "CM"))) %>% 
  mutate_at(c("bp_diastolic", "bp_systolic", "glucose", "lactate"), as.numeric) %>% # converts remaining character variables to numerics
  select(subject_id, status, everything()) %>% 
  group_by(status)

@@

           ) %>%

  ggplot(aes(x = outcome, y = cerebral_hb_tot, color = outcome)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(size = 4, alpha = 0.5,
             position = position_jitter(width = 0.1)) +
  #annotate(geom = "text", label = paste0("KW p-value = ", kw_p), x = 3, y = 350, size = 5) +
  labs(x = "", y = bquote(`Cerebral Hb`[tot])) +
  ggtitle("Outcome and NIRS-derived cerebral Hbtot in children with CM") +
  theme_bw() +
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        legend.position = "none"
        )

```

## Editor

```{r ed}

# final terms used in model
final_voi <- c("cerebral_hb_tot", "cerebral_hb_tot_alpha2", "hematocrit", "lactate")

# create df from just these variables
df_model <- df_hbox %>% 
  clean_names %>% 
  dplyr::select(c(subject_id, status, sex, all_of(final_voi))) %>% 
  filter(status != "HC")
df_model

l_hbtot_filt_brain[[10]] %>% mean(THC, na.rm = TRUE)
